Normalization: A pipeline to analyse time-course gene expression data

### 2019-05-01 scripts/01_quality_control_normalization.Rmd
Switch the California \& Kawasaki strains

# Reorder the conditions such that:
#	- Control is before any influenza treatment
#	- Each treatment is ordered from low to high pathogeny
meta$Group = factor(meta$Group, levels(meta$Group)[c(3, 1, 2, 5, 4)])

>>>>

# Reorder the conditions such that:
#	- Control is before any influenza treatment
#	- Each treatment is ordered from low to high pathogeny
meta$Group = factor(meta$Group, levels(meta$Group)[c(3, 2, 1, 5, 4)])
